### 2012-06-25 inst/examples/voi_sethi_parameters.Rmd
do all low noise, and real deterministic

@@

``` {r sethiplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

value <- melt(data.frame(stock = x_grid, det=det$V, 
                         g = g$V, m = m$V, gm = gm$V, 
                         gi = gi$V, gmi = gmi$V), id = "stock")

@@

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- names(noise) 
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

```{r }
low <- all_low
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

value <- melt(data.frame(stock = x_grid, det=det$V, low = low$V, 
                         g = g$V, m = m$V, gm = gm$V, 
                         gi = gi$V, mi=mi$V, gmi = gmi$V), id = "stock")

@@

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, true_g, true_m, true_i){

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- names(noise) 
print(xtable(matrix(means$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
````
